Simulating an Isolated Dwarf Galaxy with Energetic Feedback and Chemical Yields from Individual Stars

### 2018-04-19 main.tex
Update on Overleaf.
MNRAS style updates

%mm2 substantive changes marked with this comment tag, minor changes and wordsmithing done silently.  12-15 Feb
%mm3 since Greg has already read this, I have removed commentary as I go.  substantive changes now marked with %mm3 13 Mar 18
\documentclass[twocolumn]{aastex61}
\pdfoutput=1 %for arXiv submission
\usepackage{amsmath,amstext}
\usepackage[T1]{fontenc}
\usepackage{apjfonts} 
\usepackage[figure,figure*]{hypcap}
\usepackage{multirow}
\usepackage{mathtools}
\renewcommand*{\sectionautorefname}{Section} %for \autoref
\renewcommand*{\subsectionautorefname}{Section} %for \autoref
%\usepackage{graphicx}

@@

\shorttitle{Feedback with Individual Stars}
\shortauthors{Emerick, Bryan, Mac Low}
\newcommand{\msun}{M$_{\odot}$}
\newcommand{\ccunit}{cm$^{-3}$}

@@

\title{Simulating an Isolated Dwarf Galaxy with Energetic Feedback and Chemical Yields from Individual Stars}

\author{Andrew Emerick}
\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
\author{Greg L. Bryan}
\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}
\author{Mordecai-Mark Mac Low}
\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}

@@

\keywords{Galaxy -- Hydrodynamics -- Simulation -- Feedback}

@@

\section{Methods}
\label{sec:methods}
We produce high-resolution, galaxy-scale simulations tracking stars not as single stellar populations, but as individual stars sampled from an assumed IMF.
This allows us to follow star-by-star variations in feedback physics and stellar yields in detail. To properly model the ISM, we track non-equilibrium, primordial chemistry (including molecular hydrogen) using \texttt{Grackle} \citep{GrackleMethod}, with heating and approximate self-shielding from a metagalactic ultraviolet (UV) background. We assume collisional ionization equilibrium for all other elements and use updated \texttt{Cloudy} metal-line cooling tables consistent with our self-shielding approximation (see Appendix~\ref{appendix:cooling}). We also include an updated observationally motivated dust model for the low metallicity regimes studied here ($Z \lesssim 0.1$ Z$_{\odot}$). Each star is assigned basic properties including surface gravity, effective temperature, radius, and lifetime from tabulated stellar evolution models, which inform how the stars deposit their feedback. We directly track ionizing radiation from massive stars using an adaptive ray tracing radiative transfer method that includes the effects of radiation pressure on \ion{H}{1}. In addition, we follow the optically thin, non-ionizing UV radiation from these stars that cause photoelectric heating and Lyman-Werner dissociation of molecular hydrogen. We track the stellar wind feedback and SNe from these stars, depositing individual metal yields from both. We include AGB wind feedback and yields for lower mass stars, and track these directly as Type Ia SN progenitors. We follow yields for 15 individual metal species (C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba), chemically tagging each star as it forms with the associated local gas abundances for each species. In addition, we track a total metal density field which is the sum of all metals, including those not directly tracked. This field is used to inform the heating/cooling physics, and determines the metallicity of each star at birth. These methods are discussed in full detail below.

@@

\subsubsection{Ionizing Radiation from Discrete Sources}
\label{sec:ionizing radiation}
Radiation feedback, including ionization, ionization heating, and radiation pressure, is an important source of feedback in galaxies. \ion{H}{2} regions carved out by stellar radiation change the ISM structure in regions where SNe eventually explode, generally increasing their dynamical importance. However, accounting for angular effects, radiation can also allow energy from SNe to dissipate more readily by escaping out of channels carved through dense clouds. Radiation feedback effects have been included with various approximations in a wide range of simulations \citep[e.g.][]{OppenheimerDave2006, Krumholz2007, HopkinsQuataertMurray2012, Agertz2013, Renaud2013, Stinson2013, Roskar2014, Ceverino2014, FIRE, AgertzKravtsov2015, Forbes2016, Hu2016, Hu2017, FIRE2}, with a smaller subset using full radiation hydrodynamics \citep{WiseAbel2012,Wise2012a,Wise2014,Kim2013a, Kim2013b,Pawlik2013,Rosdahl2015,Aubert2015,Ocvirk2016,BaczynskiGloverKlessen2015,Pawlik2017} due to the additional computational expense of direct ray tracing. As we seek a complete accounting of stellar feedback physics, we follow \ion{H}{1} and \ion{He}{1} ionizing radiation from our stars through the ray tracing methods described below.

Enzo includes an adaptive ray tracing implementation, \textsc{Enzo+Moray} \citep{WiseAbel2011}, to solve the equations of radiative transfer coupled to the hydrodynamics of the simulation. We follow \ion{H}{1} and \ion{He}{1} ionizing photons which are coupled to the \texttt{Grackle} primordial chemistry and heating and cooling routines to track photoionization and heating, as well as radiation pressure on hydrogen.

We determine the \ion{H}{1} and \ion{He}{1} ionizing photon rates for each star using the OSTAR2002 \citep{Lanz2003} grid of O-type stellar models, appropriate for $M_{*} \gtrsim 15$~M$_{\odot}$ at solar metallicity\footnote{The exact stellar mass range on the OSTAR2002 grid is model dependent and a function of metallicity}. We use linear interpolation in stellar effective temperature, surface gravity, and metallicity to compute the ionizing photon fluxes and rates for each star. Stars less massive than about 15 M$_{\odot}$ and very massive stars with sub-solar metallicity are generally not well sampled by the OSTAR2002 grid. In this case, we integrate a black body spectrum at $T_{\rm eff}$ to obtain the ionizing photon fluxes, but normalize the result to be continuous with the OSTAR2002 grid (see Appendix \ref{appendix:radiation}).

@@

Instead of assigning a fixed ionizing photon energy across all sources, we integrate over each star's blackbody curve to compute the average ionizing photon energy individually for each source (see Appendix~\ref{appendix:radiation}). The average energy for \ion{H}{1} and \ion{He}{1} ionizing photons changes significantly over the OSTAR2002 temperature range $\log(T_{4,\rm{eff}} [K]) \in \left[2.75,5.5\right]$, ranging from 15.72 eV to 20.07 eV and 26.52 eV to 31.97 eV respectively.

We also include the effects of radiation pressure on \ion{H}{1}. This has been shown to be important in suppressing the star formation rates of dwarf galaxies by influencing turbulence and the dense gas content of the ISM \citep{WiseAbel2012,Ceverino2014}. We ignore the absorption of ionizing radiation by dust and re-radiation in the infrared. This is included in other models \citep[e.g.][]{Rosdahl2015,FIRE,FIRE2} as this may increase by a factor of a few to several the effective radiation pressure \citep{ZhangDavis2017}. However, the importance of multiple scattering is still unclear. Other works have shown the effect to only increase the radiation pressure by a factor of order unity \citep{Krumholz2012,Krumholz2013,Reissl2017,Wibking2018}. Due to these uncertainties, and given that our dwarf galaxy has a low dust content, and therefore a low infrared opacity, we ignore this effect.

@@

Self-shielding of gas against the metagalactic UV background is important in high-resolution simulations, particularly for low-mass, low-metallicity dwarf galaxies where the UV background is capable of gradually photoevaporating unshielded gas from the galaxy \citep{Simpson2013}. We have implemented the \citet{Rahmati2013} approximate self-shielding method in \texttt{Grackle} to account for \ion{H}{1} self-shielding against the UV background \citep[see][ for more details of this implementation]{GrackleMethod}. We assume \ion{He}{1} ionization generally follows \ion{H}{1}. This allows us to approximate \ion{He}{1} self-shielding using the same form (A. Rahmati, private communication). We ignore \ion{He}{2} photoionization from the UV background entirely. Accounting for self-shielding in this manner leads to an inconsistency in using tabulated, optically-thin metal line cooling rates from \textsc{Cloudy} (see Section 4.1.1 of \citet{Hu2017}). As mentioned previously, we have re-computed metal line cooling tables using \textsc{Cloudy} models of optically thick clouds to be consistent with our self-shielding prescription. This is described in more detail in Appendix ~\ref{appendix:cooling}.

@@

\section{Galaxy Initial Conditions}
\label{sec:IC}
We apply these methods to a first test case of the evolution of an isolated, low mass dwarf galaxy. The galaxy is constructed to have initial properties similar to those observed for the Local Group dwarf galaxy Leo P \citep{Giovanelli2013,McQuinn2013,McQuinn2015a,McQuinn2015}, although it is not intended to be a matched model to this galaxy. Leo P is gas rich, with $M_{\rm HI} = 8.1\times 10^{5}$~M$_{\odot}$ and $M_{*} = 5.6^{+0.4}_{-1.9} \times 10^{5}$~M$_{\odot}$ \citep{McQuinn2015a} extending to a radius $r_{\rm HI} = 500$~pc, and low metallicity,
with $12 + \rm{log(O/H)} = 7.17 \pm 0.04$ \citep{Skillman2013}, or a metallicity fraction of $Z/Z_{\odot} \sim 5.4\times10^{-4}$, adopting $Z_{\odot} = 0.018$ from \citet{Asplund2009}. Our dwarf galaxy model is constructed without an initial background stellar population, with a total gas mass of $1.8 \times 10^{6}$~M$_{\odot}$, of which $M_{\rm HI} = 1.35 \times 10^{6}$~M$_{\odot}$, and $Z/Z_{\odot} = 4.3\times 10^{-4}$, comparable to the average redshift $z = 0$ metallicity from the stellar models computed in \citet{McQuinn2015}.

@@

Following the initialization procedure of \citet{Hu2017}, we use artificial SN driving to generate realistic initial densities and turbulent properties in the galaxy ISM. This prevents an otherwise uniform collapse of the gas disk at the beginning of the simulation. During this period, SNe explode at a fixed rate of $0.4$~Myr$^{-1}$, corresponding to the SFR obtained given the central \ion{H}{1} surface density and the relation presented in \citep{Roychowdhury2009}. We stop the artificial driving 25~Myr after the first star particle forms. These artificial SNe do not drive chemical evolution of the galaxy; their metal yields correspond to the mean ISM abundances. We note that this initial driving is somewhat ad hoc in that we do not include any other effects from the stellar population that would have caused these SNe.

@@

\begin{figure*}
\centering
\includegraphics[width=0.975\linewidth]{multiplot_4x4_x.png}
\caption{Edge-on views of our dwarf galaxy at four different times in its evolution, 0, 150, 300, and 500 Myr after the beginning of star formation. Shown are the density weighted projection of number density (top row), temperature slices (second row), \ion{H}{1} column density (third row), and H$_2$ column density (fourth row). Each individual main sequence star particle is shown in the number density projections as a single black dot.}
\label{fig:panel_x}
\end{figure*}

@@

Constraining the gas scale height in ultra-faint dwarf galaxies observationally, to compare to our simulations, is challenging. For Leo P, located at 1.7~Mpc, \ion{H}{1} observations that are capable of detecting the diffuse \ion{H}{1} throughout the galaxy have a resolution of 100--200 pc, with higher resolution observations identifying only the densest \ion{H}{1} clumps in the galaxy \citep[e.g.][]{Bernstein-Cooper2014}.

@@

At initialization, all H and He of our dwarf galaxy is neutral, with no molecular hydrogen component. By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), \ion{H}{1} still dominates the mass of the galaxy, but a fairly significant component of molecular hydrogen has formed, with a mass of about $5.8 \times 10^5$ M$_{\odot}$, or roughly 16\%, of the total gas mass in the galaxy's disk. The total amount of molecular hydrogen mass in the system remains fairly consistent throughout the evolution, yet its fraction increases over time to roughly 35-40\%; at this point, it is about equal with the \ion{H}{1} gas. This is because the total amount of gas in the disk decreases through feedback-driven winds, but the H$_2$ is preferentially retained. Small fluctuations in the H$_2$ mass correspond with small increases in the total stellar mass, as some small fraction of H$_2$ is converted into stars, and more is destroyed from the subsequent feedback. Examining the molecular properties of the ISM in low mass dwarf galaxies in more detail is a vital avenue of future research, as there are significant observational uncertainties in deriving H$_2$ content of galaxies in this low metallicity regime \citep{Leroy2008,McQuinn2012,Amorin2016}. The molecular properties of our galaxy are discussed further in context with other works in Section~\ref{sec:observation}.

\begin{figure*}
\centering
\includegraphics[width=0.475\linewidth]{sfr_snrx100}
\includegraphics[width=0.475\linewidth]{mass_evolution}
\caption{Left: The SFR and core collapse SN rate in our dwarf galaxy in 10 Myr bins (left). Right: The evolution of the total gas mass (black), \ion{H}{1} mass (blue), H$_2$ mass (orange), and stellar mass (red) in the disk of our galaxy over time. Note that the SN rate has been scaled by a factor of 100 to fit on the same vertical axis as the SFR.}
\label{fig:sfr_mass_evolution}
\end{figure*}

@@

\begin{figure}
\centering
\includegraphics[width=0.95\linewidth]{phase_diagram.png}
\caption{The temperature vs.\ number density phase diagram of our dwarf galaxy simulation showing all gass interior to 0.25~$R_{\rm vir}$, averaged over a 50~Myr period from t~=~300~Myr to t~=~350~Myr. The two red dashed lines show lines of constant pressure for guidance. The region in the lower right corner indicates our density and temperature thresholds for star formation.}
\label{fig:phase}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[width=0.45\linewidth]{phase_mass_fraction_evolution_log.png}
\includegraphics[width=0.45\linewidth]{phase_volume_fraction_evolution_log.png}
\caption{The evolution of the mass and volume fractions for each phase of the model galaxy's ISM.}
\label{fig:ISM_evolution}
\end{figure*}

@@

\begin{figure}
\includegraphics[width=0.95\linewidth]{G_o_profile} \\
\includegraphics[width=0.95\linewidth]{ionizing_photon_profile}
\caption{
Azimuthally averaged radial profiles of the ISRF in the mid-plane of our galaxy in two different bands, time-averaged over 50 Myr from 300 -- 350~Myr. Here we define the midplane as within 2.5~$dx$ of z = 0, or 4.5~pc. The top panel gives $G_{\rm o}$, the flux of radiation between 6--13.6 eV normalized to the value in the solar neighborhood, shaded between minimum and maximum values at each position, with the average shown as a black line. The bottom panel gives the \ion{H}{1} ionizing stellar radiation flux. Since this radiation is tracked directly through radiative transfer, the minimum value at all radii is 0 at some point. For this reason we only shade between the first quartile and maximum values. \ion{He}{1} ionizing radiation is very similar to \ion{H}{1} ionizing radiation, with a small vertical offset, and is not shown for clarity.}
\label{fig:ISRF}
\end{figure}

The bottom panel gives the ionizing photon fluxes for \ion{H}{1} from stellar radiation {\em only}. Since this field is tracked directly using ray-tracing radiative transfer, the profile encodes information about local attenuation of these photons from dense, neutral gas. This is the main driver of the differences between this field and $G_{\rm o}$. However, both profiles track each other well as a function of radius. The lack of dramatic trend with radius in both diagrams suggests that one could model the ISRF in low mass dwarf galaxies using a uniform heating / ionization rate; however, this would still fail to capture the fact that any given region of the galaxy will experience order of magnitude or more fluctuations in the incident flux.

\begin{figure*}
\centering
\includegraphics[width=0.45\linewidth]{g_o_2D_phase}
\includegraphics[width=0.45\linewidth]{q_o_2D_phase}
\caption{Single-snapshot 2D radial profile plots at 200~Myr of the ISRF in two flux bands, $G_{\rm o}$ and \ion{H}{1} ionizing radiation, illustrating the full dynamic range of radiation flux at a given radius in the galaxy. Here, we include all gas within the mid-plane of our dwarf galaxy. Since a majority of the mass of the galaxy is in the cold phase (see Figure~\ref{fig:phase}), and is therefore optically thick to \ion{H}{1} ionizing radiation, it does not show up in the \ion{H}{1} ionizing radiation diagram. This gas readily appears in the $G_{\rm o}$ diagram since we assume it to be optically thin, though we do apply a localized shielding approximation.}
\label{fig:ISRF_2D}
\end{figure*}

>>>>

%mm2 substantive changes marked with this comment tag, minor changes and wordsmithing done silently.  12-15 Feb
%mm3 since Greg has already read this, I have removed commentary as I go.  substantive changes now marked with %mm3 13 Mar 18
%\documentclass[twocolumn]{aastex61}
%\pdfoutput=1 %for arXiv submission
\documentclass[a4paper,fleqn,usenatbib,useAMS]{mnras}
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}        % Multi-column entries in tables
\usepackage{bm}		% Bold maths symbols, including upright Greek
%\usepackage{pdflscape}	% Landscape pages

\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{newtxtext,newtxmath}

%\usepackage{amsmath,amstext}
%\usepackage[T1]{fontenc}
\usepackage[figure,figure*]{hypcap}
%\usepackage{multirow}
%\usepackage{mathtools}
%\renewcommand*{\sectionautorefname}{Section} %for \autoref
%\renewcommand*{\subsectionautorefname}{Section} %for \autoref
%\usepackage{graphicx}

%\usepackage{apjfonts} 
%\usepackage{natbib} % bibliography

@@

%\shorttitle{Feedback with Individual Stars}
%\shortauthors{Emerick, Bryan, Mac Low}
\newcommand{\msun}{M$_{\odot}$}
\newcommand{\ccunit}{cm$^{-3}$}

% For bibtex

\title[Feedback with Individual Stars]{Simulating an Isolated Dwarf Galaxy with Energetic Feedback and Chemical Yields from Individual Stars}

\author[A. Eemerick et. al.]{
Andrew Emerick,$^{1,2}$
Greg L. Bryan,$^{1,3}$
and Mordecai-Mark Mac Low$^{2,1}$
\\
$^{1}$Department of Astronomy, Columbia University, New York, NY, 10027, USA\\
$^{2}$Department of Astrophysics, American Museum of Natural History, New York, NY, USA\\
$^{3}$Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}

@@

\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle
%\title{Simulating an Isolated Dwarf Galaxy with Energetic Feedback and Chemical Yields from Individual Stars}

%\author{Andrew Emerick}
%\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
%\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
%\author{Greg L. Bryan}
%\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
%\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}
%\author{Mordecai-Mark Mac Low}
%\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
%\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}

@@

\begin{keywords}
Galaxy -- Hydrodynamics -- Simulation -- Feedback
\end{keywords}

@@

\section{Methods}
\label{sec:methods}
We produce high-resolution, galaxy-scale simulations tracking stars not as single stellar populations, but as individual stars sampled from an assumed IMF.
This allows us to follow star-by-star variations in feedback physics and stellar yields in detail. To properly model the ISM, we track non-equilibrium, primordial chemistry (including molecular hydrogen) using \texttt{Grackle} \citep{GrackleMethod}, with heating and approximate self-shielding from a metagalactic ultraviolet (UV) background. We assume collisional ionization equilibrium for all other elements and use updated \texttt{Cloudy} metal-line cooling tables consistent with our self-shielding approximation (see Appendix~\ref{appendix:cooling}). We also include an updated observationally motivated dust model for the low metallicity regimes studied here ($Z \lesssim 0.1$ Z$_{\odot}$). Each star is assigned basic properties including surface gravity, effective temperature, radius, and lifetime from tabulated stellar evolution models, which inform how the stars deposit their feedback. We directly track ionizing radiation from massive stars using an adaptive ray tracing radiative transfer method that includes the effects of radiation pressure on HI. In addition, we follow the optically thin, non-ionizing UV radiation from these stars that cause photoelectric heating and Lyman-Werner dissociation of molecular hydrogen. We track the stellar wind feedback and SNe from these stars, depositing individual metal yields from both. We include AGB wind feedback and yields for lower mass stars, and track these directly as Type Ia SN progenitors. We follow yields for 15 individual metal species (C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba), chemically tagging each star as it forms with the associated local gas abundances for each species. In addition, we track a total metal density field which is the sum of all metals, including those not directly tracked. This field is used to inform the heating/cooling physics, and determines the metallicity of each star at birth. These methods are discussed in full detail below.

@@

\subsubsection{Ionizing Radiation from Discrete Sources}
\label{sec:ionizing radiation}
Radiation feedback, including ionization, ionization heating, and radiation pressure, is an important source of feedback in galaxies. \ion{H}{2} regions carved out by stellar radiation change the ISM structure in regions where SNe eventually explode, generally increasing their dynamical importance. However, accounting for angular effects, radiation can also allow energy from SNe to dissipate more readily by escaping out of channels carved through dense clouds. Radiation feedback effects have been included with various approximations in a wide range of simulations \citep[e.g.][]{OppenheimerDave2006, Krumholz2007, HopkinsQuataertMurray2012, Agertz2013, Renaud2013, Stinson2013, Roskar2014, Ceverino2014, FIRE, AgertzKravtsov2015, Forbes2016, Hu2016, Hu2017, FIRE2}, with a smaller subset using full radiation hydrodynamics \citep{WiseAbel2012,Wise2012a,Wise2014,Kim2013a, Kim2013b,Pawlik2013,Rosdahl2015,Aubert2015,Ocvirk2016,BaczynskiGloverKlessen2015,Pawlik2017} due to the additional computational expense of direct ray tracing. As we seek a complete accounting of stellar feedback physics, we follow HI and HeI ionizing radiation from our stars through the ray tracing methods described below.

Enzo includes an adaptive ray tracing implementation, \textsc{Enzo+Moray} \citep{WiseAbel2011}, to solve the equations of radiative transfer coupled to the hydrodynamics of the simulation. We follow HI and HeI ionizing photons which are coupled to the \texttt{Grackle} primordial chemistry and heating and cooling routines to track photoionization and heating, as well as radiation pressure on hydrogen.

We determine the HI and HeI ionizing photon rates for each star using the OSTAR2002 \citep{Lanz2003} grid of O-type stellar models, appropriate for $M_{*} \gtrsim 15$~M$_{\odot}$ at solar metallicity\footnote{The exact stellar mass range on the OSTAR2002 grid is model dependent and a function of metallicity}. We use linear interpolation in stellar effective temperature, surface gravity, and metallicity to compute the ionizing photon fluxes and rates for each star. Stars less massive than about 15 M$_{\odot}$ and very massive stars with sub-solar metallicity are generally not well sampled by the OSTAR2002 grid. In this case, we integrate a black body spectrum at $T_{\rm eff}$ to obtain the ionizing photon fluxes, but normalize the result to be continuous with the OSTAR2002 grid (see Appendix \ref{appendix:radiation}).

@@

Instead of assigning a fixed ionizing photon energy across all sources, we integrate over each star's blackbody curve to compute the average ionizing photon energy individually for each source (see Appendix~\ref{appendix:radiation}). The average energy for HI and HeI ionizing photons changes significantly over the OSTAR2002 temperature range $\log(T_{4,\rm{eff}} [K]) \in \left[2.75,5.5\right]$, ranging from 15.72 eV to 20.07 eV and 26.52 eV to 31.97 eV respectively.

We also include the effects of radiation pressure on HI. This has been shown to be important in suppressing the star formation rates of dwarf galaxies by influencing turbulence and the dense gas content of the ISM \citep{WiseAbel2012,Ceverino2014}. We ignore the absorption of ionizing radiation by dust and re-radiation in the infrared. This is included in other models \citep[e.g.][]{Rosdahl2015,FIRE,FIRE2} as this may increase by a factor of a few to several the effective radiation pressure \citep{ZhangDavis2017}. However, the importance of multiple scattering is still unclear. Other works have shown the effect to only increase the radiation pressure by a factor of order unity \citep{Krumholz2012,Krumholz2013,Reissl2017,Wibking2018}. Due to these uncertainties, and given that our dwarf galaxy has a low dust content, and therefore a low infrared opacity, we ignore this effect.

@@

Self-shielding of gas against the metagalactic UV background is important in high-resolution simulations, particularly for low-mass, low-metallicity dwarf galaxies where the UV background is capable of gradually photoevaporating unshielded gas from the galaxy \citep{Simpson2013}. We have implemented the \citet{Rahmati2013} approximate self-shielding method in \texttt{Grackle} to account for HI self-shielding against the UV background \citep[see][ for more details of this implementation]{GrackleMethod}. We assume HeI ionization generally follows HI. This allows us to approximate HeI self-shielding using the same form (A. Rahmati, private communication). We ignore HeII photoionization from the UV background entirely. Accounting for self-shielding in this manner leads to an inconsistency in using tabulated, optically-thin metal line cooling rates from \textsc{Cloudy} (see Section 4.1.1 of \citet{Hu2017}). As mentioned previously, we have re-computed metal line cooling tables using \textsc{Cloudy} models of optically thick clouds to be consistent with our self-shielding prescription. This is described in more detail in Appendix ~\ref{appendix:cooling}.

@@

\section{Galaxy Initial Conditions}
\label{sec:IC}
We apply these methods to a first test case of the evolution of an isolated, low mass dwarf galaxy. The galaxy is constructed to have initial properties similar to those observed for the Local Group dwarf galaxy Leo P \citep{Giovanelli2013,McQuinn2013,McQuinn2015a,McQuinn2015}, although it is not intended to be a matched model to this galaxy. Leo P is gas rich, with $M_{\rm HI} = 8.1\times 10^{5}$~M$_{\odot}$ and $M_{*} = 5.6^{+0.4}_{-1.9} \times 10^{5}$~M$_{\odot}$ \citep{McQuinn2015a} extending to a radius $r_{\rm HI} = 500$~pc, and low metallicity,
with $12 + \rm{log(O/H)} = 7.17 \pm 0.04$ \citep{Skillman2013}, or a metallicity of $Z \sim 5.4\times10^{-4}$ ($Z/Z_{\odot} = 0.03$, adopting $Z_{\odot} = 0.018$ from \citet{Asplund2009}). Our dwarf galaxy model is constructed without an initial background stellar population, with a total gas mass of $1.8 \times 10^{6}$~M$_{\odot}$, of which $M_{\rm HI} = 1.35 \times 10^{6}$~M$_{\odot}$, and $Z = 4.3\times 10^{-4}$, comparable to the average redshift $z = 0$ metallicity from the stellar models computed in \citet{McQuinn2015}.

@@

Following the initialization procedure of \citet{Hu2017}, we use artificial SN driving to generate realistic initial densities and turbulent properties in the galaxy ISM. This prevents an otherwise uniform collapse of the gas disk at the beginning of the simulation. During this period, SNe explode at a fixed rate of $0.4$~Myr$^{-1}$, corresponding to the SFR obtained given the central HI surface density and the relation presented in \citep{Roychowdhury2009}. We stop the artificial driving 25~Myr after the first star particle forms. These artificial SNe do not drive chemical evolution of the galaxy; their metal yields correspond to the mean ISM abundances. We note that this initial driving is somewhat ad hoc in that we do not include any other effects from the stellar population that would have caused these SNe.

@@

\begin{figure*}
\centering
\includegraphics[width=0.975\linewidth]{multiplot_4x4_x.png}
\caption{Edge-on views of our dwarf galaxy at four different times in its evolution, 0, 150, 300, and 500 Myr after the beginning of star formation. Shown are the density weighted projection of number density (top row), temperature slices (second row), HI column density (third row), and H$_2$ column density (fourth row). Each individual main sequence star particle is shown in the number density projections as a single black dot.}
\label{fig:panel_x}
\end{figure*}

@@

Constraining the gas scale height in ultra-faint dwarf galaxies observationally, to compare to our simulations, is challenging. For Leo P, located at 1.7~Mpc, HI observations that are capable of detecting the diffuse HI throughout the galaxy have a resolution of 100--200 pc, with higher resolution observations identifying only the densest HI clumps in the galaxy \citep[e.g.][]{Bernstein-Cooper2014}.

@@

At initialization, all H and He of our dwarf galaxy is neutral, with no molecular hydrogen component. By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), HI still dominates the mass of the galaxy, but a fairly significant component of molecular hydrogen has formed, with a mass of about $5.8 \times 10^5$ M$_{\odot}$, or roughly 16\%, of the total gas mass in the galaxy's disk. The total amount of molecular hydrogen mass in the system remains fairly consistent throughout the evolution, yet its fraction increases over time to roughly 35-40\%; at this point, it is about equal with the HI gas. This is because the total amount of gas in the disk decreases through feedback-driven winds, but the H$_2$ is preferentially retained. Small fluctuations in the H$_2$ mass correspond with small increases in the total stellar mass, as some small fraction of H$_2$ is converted into stars, and more is destroyed from the subsequent feedback. Examining the molecular properties of the ISM in low mass dwarf galaxies in more detail is a vital avenue of future research, as there are significant observational uncertainties in deriving H$_2$ content of galaxies in this low metallicity regime \citep{Leroy2008,McQuinn2012,Amorin2016}. The molecular properties of our galaxy are discussed further in context with other works in Section~\ref{sec:observation}.

\begin{figure*}
\centering
\includegraphics[width=0.475\linewidth]{sfr_snrx100}
\includegraphics[width=0.475\linewidth]{mass_evolution}
\caption{Left: The SFR and core collapse SN rate in our dwarf galaxy in 10 Myr bins (left). Right: The evolution of the total gas mass (black), HI mass (blue), H$_2$ mass (orange), and stellar mass (red) in the disk of our galaxy over time. Note that the SN rate has been scaled by a factor of 100 to fit on the same vertical axis as the SFR.}
\label{fig:sfr_mass_evolution}
\end{figure*}

@@

\begin{figure}
%\centering
\includegraphics[width=0.95\linewidth]{phase_diagram.png}
\caption{The temperature vs.\ number density phase diagram of our dwarf galaxy simulation showing all gass interior to 0.25~$R_{\rm vir}$, averaged over a 50~Myr period from t~=~300~Myr to t~=~350~Myr. The two red dashed lines show lines of constant pressure for guidance. The region in the lower right corner indicates our density and temperature thresholds for star formation.}
\label{fig:phase}
\end{figure}

@@

\begin{figure*}
%\centering
\includegraphics[width=0.45\linewidth]{phase_mass_fraction_evolution_log.png}
\includegraphics[width=0.45\linewidth]{phase_volume_fraction_evolution_log.png}
\caption{The evolution of the mass and volume fractions for each phase of the model galaxy's ISM.}
\label{fig:ISM_evolution}
\end{figure*}

@@

\begin{figure}
\includegraphics[width=0.95\linewidth]{G_o_profile} \\
\includegraphics[width=0.95\linewidth]{ionizing_photon_profile}
\caption{
Azimuthally averaged radial profiles of the ISRF in the mid-plane of our galaxy in two different bands, time-averaged over 50 Myr from 300 -- 350~Myr. Here we define the midplane as within 2.5~$dx$ of z = 0, or 4.5~pc. The top panel gives $G_{\rm o}$, the flux of radiation between 6--13.6 eV normalized to the value in the solar neighborhood, shaded between minimum and maximum values at each position, with the average shown as a black line. The bottom panel gives the HI ionizing stellar radiation flux. Since this radiation is tracked directly through radiative transfer, the minimum value at all radii is 0 at some point. For this reason we only shade between the first quartile and maximum values. HeI ionizing radiation is very similar to HI ionizing radiation, with a small vertical offset, and is not shown for clarity.}
\label{fig:ISRF}
\end{figure}

The bottom panel gives the ionizing photon fluxes for HI from stellar radiation {\em only}. Since this field is tracked directly using ray-tracing radiative transfer, the profile encodes information about local attenuation of these photons from dense, neutral gas. This is the main driver of the differences between this field and $G_{\rm o}$. However, both profiles track each other well as a function of radius. The lack of dramatic trend with radius in both diagrams suggests that one could model the ISRF in low mass dwarf galaxies using a uniform heating / ionization rate; however, this would still fail to capture the fact that any given region of the galaxy will experience order of magnitude or more fluctuations in the incident flux.

\begin{figure*}
%\centering
\includegraphics[width=0.45\linewidth]{g_o_2D_phase}
\includegraphics[width=0.45\linewidth]{q_o_2D_phase}
\caption{Single-snapshot 2D radial profile plots at 200~Myr of the ISRF in two flux bands, $G_{\rm o}$ and HI ionizing radiation, illustrating the full dynamic range of radiation flux at a given radius in the galaxy. Here, we include all gas within the mid-plane of our dwarf galaxy. Since a majority of the mass of the galaxy is in the cold phase (see Figure~\ref{fig:phase}), and is therefore optically thick to HI ionizing radiation, it does not show up in the HI ionizing radiation diagram. This gas readily appears in the $G_{\rm o}$ diagram since we assume it to be optically thin, though we do apply a localized shielding approximation.}
\label{fig:ISRF_2D}
\end{figure*}

To further quantify the local variations in these radiation fields, we present the full distribution of $G_{\rm o}$ and the HI ionizing flux in Figure~\ref{fig:ISRF_2D} at a single snapshot at 200~Myr. This diagram shows how dramatic the increase in ISRF near young, massive stars is (the spikes in both diagrams), while much of the mid-plane sees an ISRF orders of magnitude lower. The striking contrast between the two diagrams is due to the shielding of the HI ionizing flux in the most massive (cold and dense) regions of the galaxy through the radiative transfer calculations; shielding of the FUV radiation is approximate and in general weaker, making these regions more prominent in the left hand figure (the pink/white clumps). From both of these diagrams, it is clear that the ISRF of a low mass dwarf galaxy varies greatly over time and space in a way that cannot be appropriately captured by an analytic profile. Although one could adopt an averaged radial profile to provide a realistic, global source of energy for thermal pressure support of the gas against collapse, it is unclear how sufficient this would be in suppressing star formation. In particular, the large increases around sites of recent star formation could be important sources of feedback to destroy molecular clouds and reduce their effective star formation efficiency. It remains to be seen which of these two modes of feedback is more important in regulating star formation.
